\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-20 Articles/IROS/root.tex
fixes page 2

By multiplieing weights components for primary and both orthagonal axis we get matrix kernels. We get one kernel for every cartesian direction.

@@

The occupancy grid's representation of the robot's environment is inherently discrete, possessing finite resolution, in contrast to the continuous nature of Cartesian space. The approximation or rounding necessary to transition from Cartesian coordinates to discrete grid representations may introduce discontinuities in the calculated repulsive field. To counteract this, tri-linear interpolation is utilized, facilitating a smooth transition to a continuous repulsive field value, as illustrated in Fig. \ref{fig:interp-experiment}.

@@

Trilinear interpolation method works on a 3-dimensional regular grid. Before we can start with the interpolation we need to calculate the distance between POI and smaller coordinates of the cells where we calculated the repulsive velocities (eq.~\ref{eq: deltas interp}). The calculated repulsive velocity values are located at the centers of the cells. Therefore, before interpolation, we shift the values of the cells coordinates by half the resolution of the obstacle grid in each direction. That is, the cell coordinates are same as $x,y,z$, cell index and a half multiplied by grid resolution $\Delta \mathrm{R}$.

>>>>

By multiplieing weights components for primary and both orthagonal axis we get matrix kernels. We calculate a different kernel for every cartesian direction.

@@

The occupancy grid's representation of the robot's environment is inherently discrete, possessing finite resolution, in contrast to the continuous nature of Cartesian space. The approximation or rounding necessary to transition from Cartesian coordinates to discrete grid representations introduces discontinuities in the calculated repulsive field. To counteract this, tri-linear interpolation is utilized, facilitating a smooth transition to a continuous repulsive field value, as illustrated in Fig. \ref{fig:interp-experiment}.

@@

Trilinear interpolation method works on a 3-dimensional regular grid. Before we can start with the interpolation we need to calculate the distance between POI and smaller coordinates of the cells where we calculated the repulsive velocities (eq.~\ref{eq: deltas interp}). The calculated repulsive velocity values are located at the centers of the cells. Therefore, before interpolation, we shift the values of the cells coordinates by half the resolution of the obstacle grid in each direction. That is, the cell coordinates are same as $x,y,z$, cell index and plus a half of grid resolution $\Delta \mathrm{R}$ step.
